Revision Plan for SIGCOMM'24 Paper \#293

### 2024-05-22 revision_plan.tex
update

\noindent Thank you for shepherding our paper (\textit{\#293 PPT: A Pragmatic Transport for Datacenters}). 
We carefully went through the reviews and outlined our revision plan.\\

@@

\textcolor{blue}{Finally, the PPT prototype implementation, te CloudLab testbed experiments and the comments about the issues in Homa-Linux implementation verify that PPT is a readily deployable solution.
}

@@

\noindent\textcolor{blue}{\textbf{Response 2:} PCC Proteus is radically different with PPT.
First, PCC Proteus is designed for Internet while our PPT is used for datacenter network environment.
Second, PCC Proteus depends on application requirements and use the traffic of low-priority applications to fill the bandwidth leftover by high-priority application. PPT uses different bandwidth padding scheme. That said, it does not rely on application's priority or requirement. It instead uses the opportunistic packets starting from the end of the same flow to fill the spare bandwidth in the network.
Finally, PCC Proteus requires application to specify its priorities, while PPT gradually demotes a flow's priority as more bytes sent. We will plan to discuss PCC Proteus and other related work in Appendix B.}

@@

\noindent\textcolor{blue}{\textbf{Response 4:} 
We actually are not claiming that "integration with other transports is easy"
What we claim is that the design of PPT can be integrated with delay-based transport.
We have already justified this point in our submission.
First, we have already implemented a delay-based transport conceptually equivalent to Swift in the ns3 simulator and showed that PPT's design can improve the performance of the original delay-based transport. Please see Fig. 26 for more details.
On the other hand, we have also discussed about the compatibility of PPT with other transports. Please see Appendix A for more details.
}

@@

\textcolor{blue}{Finally, the PPT prototype implementation, te CloudLab testbed experiments and the comments about the issues in Homa-Linux implementation verify that PPT is a readily deployable solution.
}

@@

\textcolor{blue}{We would like to clarify the goals of PPT uses such priority queues is to optimize the performance of small flows. This design motivated by PPT's dual-loop rate control treats all flows equally in the network. Specifically, the packets of small flows may be queued after those of large flows. Therefore, PPT uses a mirror-symmetric packet tagging method which makes PPT achieve comparable small flow performance with Homa. We plan to add more text in Sec.4 to clarify these point.
}

@@

\noindent\textcolor{blue}{\textbf{Response A.4}
PPT's large flow performance benefits from the following points. 
First, DCTCP contains spare bandwidth in slow start phase, which is obvious.
Second, in queue build-up phase, DCTCP also contains some spare bandwidth. We have already shown that DCTCP leaves nearly half of the bandwidth under-utilized. Please see Fig.1 for more details.
Finally, filling the gap of DCTCP to MW utilized the spare bandwith gracefully. We have already demonstrated by experiment that filling the DCTCP gap achieves better performance than Homa and NDP.
Further, we show via an experiment that MW is the optimal value for filling the spare bandwidth.
Please see Fig. 1 and Fig. 2 in Section 2.3 for more details.
These make PPT achieve a better large flow performance.
}

@@

\noindent\textcolor{blue}{\textbf{Response A.5}
PPT actually will not send the opportunity packet when 10 more flows arrive.
Specifically, traffic bursts result in more ECN-marked packets.
The value of $\alpha$ increases due to Eq. (1), when PPT will not send any opportunity packets.
}

\textcolor{blue}{We have already run a simulation and shown when there are multiple concurrent flows, DCTCP may cut windows simultaneously, thus causing a sudden drain on the switch buffer and leaving bandwidth underutilized. Please see Fig.1 for more details.}

\textcolor{blue}{DCTCP leaves significant spare bandwidth as it ramps up to the maximum window. So, PPT fills the spare bandwidth by sending low-priority opportunity packets. Even if the link is fully utilized, it can be rapidly backtracked to DCTCP by dropping low-priority opportunity packets.}

@@

\noindent\textcolor{blue}{\textbf{Response D.1}
DCTCP is widely deployed and used as the default congestion control algorithm in linux kernel for many years.
Therefore, DCTCP has fewer barriers to adoption and a broader reach compared to other transport protocols.
Moreover, through experiments, we have already demonstrated that DCTCP achieves performance comparable to state-of-the-art proactive transports when utilizing spare bandwidth.
Please see Section 2.3 for more details.
These support PPT to design based on DCTCP.
}

@@

\noindent\textcolor{blue}{\textbf{Response D.2}
We will add the analysis of delay-based transports to Table 1.
Swift's variant actually doesn't include the component that handles endpoint congestion.
}

@@

\noindent\textcolor{blue}{\textbf{Response E.2}
PPT's HCP is exactly DCTCP. So, PPT can coexist with the TCP family of transports friendly.
To be frank, we have not taken into account the fairness issue.
We will discuss this point in Appendix A.
}

>>>>

\noindent Thank you for shepherding our paper (\textit{\#293 PPT: A Pragmatic Transport for Datacenters}). 
We carefully went through the reviews and outlined our revision plan (as detailed below).\\

@@

\textcolor{blue}{Finally, the PPT prototype implementation, the CloudLab testbed experiments and the comments about the issues in Homa-Linux implementation verify that PPT is a readily deployable solution.
}

@@

\noindent\textcolor{blue}{\textbf{Response 2:} PCC Proteus is radically different with PPT.
First, PCC Proteus is designed for Internet while our PPT is used for datacenter network environment.
Second, PCC Proteus depends on application requirements and use the traffic of low-priority applications to fill the bandwidth leftover by high-priority application. PPT uses different bandwidth padding scheme. That said, it does not rely on application's priority or requirement. It instead uses the opportunistic packets starting from the end of the same flow to fill the spare bandwidth in the network.
Finally, PCC Proteus requires application to specify its priorities, while PPT gradually demotes a flow's priority as more bytes sent. We plan to discuss PCC Proteus and other related work in Appendix B.}

@@

\noindent\textcolor{blue}{\textbf{Response 4:} 
We actually are not claiming that ``integration with other transports is easy".
What we claim is that the design of PPT can be integrated with delay-based transport.
We have already justified this point in our submission.
First, we have already implemented a delay-based transport conceptually equivalent to Swift in the ns3 simulator and showed that PPT's design can improve the performance of the original delay-based transport. Please see Fig. 26 for more details.
On the other hand, we have also discussed about the compatibility of PPT with other transports. Please see Appendix A for more details.
}

@@

%\textcolor{blue}{Finally, the PPT prototype implementation, te CloudLab testbed experiments and the comments about the issues in Homa-Linux implementation verify that PPT is a readily deployable solution.
%}

@@

\textcolor{blue}{On the other hand, as we have shown in the above response, the priority queuing design does not affect the primary goal of optimizing the overall average FCT of flows. It is an add-on design on the parallel control loop to further optimize the average FCT of small flows.
}

%\textcolor{blue}{We would like to clarify the goals of PPT uses such priority queues is to optimize the performance of small flows. This design motivated by PPT's dual-loop rate control treats all flows equally in the network. Specifically, the packets of small flows may be queued after those of large flows. Therefore, PPT uses a mirror-symmetric packet tagging method which makes PPT achieve comparable small flow performance with Homa. We plan to add more text in Sec.4 to clarify these point.
%}

@@

\noindent\textcolor{blue}{\textbf{Response A.4}
Yes. PPT's large flow's performance benefit is mainly because PPT can dynamically identify and fill the spare bandwidth in the network.
Besides, the use of priorities is mainly for flow scheduling to further optimize the performance of small flows by prioritizing the packets of small flows over those of large ones in switch buffer. 
We have already verified these points in design space section (Sec. 2.3).}

\textcolor{blue}{Regarding the 4 classes (or priorities) of traffic, we have already claimed in the above response that we are not simply dividing the traffic into four class of flows and coupling flows with different priorities to utilize the spare bandwidth. Instead, we divide each individual flow into two parts: the first part runs with high priorities while the second part runs with low priorities to utilize the spare bandwidth in the network. 
So, it makes little sense to compare PPT with an algorithm that has 4 priorities with DCTCP or HPCC in each.
But we do have already compared PPT with HPCC directly and the results demonstrated that PPT outperforms HPCC. Please see Fig. 16 for more details. }

%\noindent\textcolor{blue}{
%PPT's large flow performance benefits from the following points. 
%First, DCTCP contains spare bandwidth in slow start phase, which is obvious.
%Second, in queue build-up phase, DCTCP also contains some spare bandwidth. We have already shown that DCTCP leaves nearly half of the bandwidth under-utilized. Please see Fig.1 for more details.
%Finally, filling the gap of DCTCP to MW utilized the spare bandwith gracefully. We have already demonstrated by experiment that filling the DCTCP gap achieves better performance than Homa and NDP.
%Further, we show via an experiment that MW is the optimal value for filling the spare bandwidth.
%Please see Fig. 1 and Fig. 2 in Section 2.3 for more details.
%These make PPT achieve a better large flow performance.
%}

@@

\noindent\textcolor{blue}{\textbf{Response A.5}
Thanks for the reviewer's very good comments.
This is really a good question and a very extreme example.
Let's rephrase the example the reviewer mentioned. Saying that there is a flow 1 that is currently using the full link bandwidth. Then, another 10 flows (flow 2,$\cdots$,11) arrive.
In this case, the opportunistic packets for flow 1 will not be sent, because queue build-up forms and more ECN-marked packets will be exhibited by flow 1, thus leading the value of its $\alpha$ keep increasing. Whereas, PPT only initialize an LCP loop and send opportunistic packet for a flow when its $\alpha$ takes minimum value.}

\textcolor{blue}{
On the other hand, PPT will open an LCP loop for each of the flow in flows 2$\sim$11 (if they are identified as small flows) to let them send opportunistic packets. However, these opportunistic packets may be queued or dropped due to buffer overflow, thus their LCP loops will be closed in a short while.
} 
%PPT actually will not send the opportunity packet when 10 more flows arrive.
%Specifically, traffic bursts result in more ECN-marked packets.
%The value of $\alpha$ increases due to Eq. (1), when PPT will not send any opportunity packets.

%\textcolor{blue}{We have already run a simulation and shown when there are multiple concurrent flows, DCTCP may cut windows simultaneously, thus causing a sudden drain on the switch buffer and leaving bandwidth underutilized. Please see Fig.1 for more details.}
%
%\textcolor{blue}{DCTCP leaves significant spare bandwidth as it ramps up to the maximum window. So, PPT fills the spare bandwidth by sending low-priority opportunity packets. Even if the link is fully utilized, it can be rapidly backtracked to DCTCP by dropping low-priority opportunity packets.}

@@

\noindent\textcolor{blue}{\textbf{Response D.1}
Thanks for the reviewer's good comments.
In fact, DCTCP is widely deployed in production and used as the default congestion control algorithm in linux kernel for many years.
Therefore, DCTCP has fewer barriers to adoption and a broader reach compared to other transport protocols.
Moreover, through our design and experiments, we have already demonstrated that we can achieve good performance by utilizing the spare bandwidth of DCTCP, while retaining the compatibility with legacy TCP/IP network stacks.
These factors motivate us to design an add-on system on DCTCP.
}

@@

\noindent\textcolor{blue}{\textbf{Response D.2}
Thanks for the comments. We will add the discussions with Timely and Swift in Related Work section (Appendix B).
By the way, Swift's variant actually doesn't include the component that handles endpoint congestion. We will clarify this in Appendix C.3.
}

@@

\noindent\textcolor{blue}{\textbf{Response E.2}
PPT's HCP is exactly DCTCP. So, PPT is essentially a TCP-friendly design.
Regarding the fairness issue, frankly speaking, we have not taken it into account.
We plan to discuss it in Appendix A.
}
